A fast and Low-Overhead Technique to Secure Programs Against Integer Overflows

### 2012-09-05 doc/Manuscript/CGO/paper.tex

@@

%Analysis about the Table 1 of the spreadsheet (Unpruned Instrumentation)
Figure~\ref{fig:unpruned_analysis} shows the number of instructions that has
received instrumentation, without avoiding inserting the instrumentation by
using any static analysis. We can see that the number of these instructions is low 
(3,96 in the average). 
Figure~\ref{fig:prunning_analysis} shows that it is possible to use static 
analysis to avoid inserting the instrumentation in some instructions.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Static Analysis
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Analysis about the amount of instructions
\begin{figure*}[t!]
\begin{center}
\begin{small}
\begin{tabular}{|l|r|r|r|r|}
\hline
Program Name & \multicolumn{1}{l|}{Num. of Instructions} & \multicolumn{1}{l|}{Num. Instrumented Instructions} & \multicolumn{1}{l|}{Perc. Instrumented Instructions} & \multicolumn{1}{l|}{Num. Instructions Where Overflows Occurred} \\ \hline
470.lbm & 13.724 & 1.142 & 8,32\% & 0 \\ \hline
433.milc & 44.236 & 1.602 & 3,62\% & 11 \\ \hline
444.namd & 100.276 & 3.234 & 3,23\% & 12 \\ \hline
447.dealII & 1.381.408 & 36.157 & 2,62\% & 50 \\ \hline
450.soplex & 136.367 & 3.158 & 2,32\% & 13 \\ \hline
464.h264ref & 271.627 & 13.846 & 5,10\% & 167 \\ \hline
473.astar & 19.243 & 857 & 4,45\% & 0 \\ \hline
458.sjeng & 54.051 & 2.504 & 4,63\% & 68 \\ \hline
429.mcf & 4.725 & 165 & 3,49\% & 8 \\ \hline
471.omnetpp & 203.201 & 1.972 & 0,97\% & 2 \\ \hline
403.gcc & 1.419.456 & 18.669 & 1,32\% & N/A \\ \hline
445.gobmk & 308.475 & 14.129 & 4,58\% & 4 \\ \hline
462.libquantum & 16.297 & 928 & 5,69\% & 7 \\ \hline
401.bzip2 & 38.831 & 2.158 & 5,56\% & N/A \\ \hline
456.hmmer & 114.136 & 4.001 & 3,51\% & 0 \\ \hline
\multicolumn{1}{|r|}{Total (Average)} & 275.070 & 6.968 & 3,96\% &  \\ \hline
\end{tabular}
\end{small}
\end{center}
\caption{\label{fig:unprunedTable}
Unpruned analysis.}
\end{figure*}

%Prunning analysis
\begin{figure*}[t!]
\begin{center}
\begin{small}
\begin{tabular}{|l|r|r|r|r|r|}
\hline
Name & \multicolumn{1}{l|}{Num. instrumented instructions} & \multicolumn{1}{l|}{Num. instrumented instructions with e-SSA form} & \multicolumn{1}{l|}{Perc. reduction of e-SSA compared with original} & \multicolumn{1}{l|}{Num. instrumented instructions with u-SSA form} & \multicolumn{1}{l|}{Perc. reduction of u-SSA compared with original} \\ \hline
470.lbm & 1.142 & 4 & 99,65\% & 4 & 99,65\% \\ \hline
433.milc & 1.573 & 1.070 & 31,98\% & 1.065 & 32,29\% \\ \hline
444.namd & 2.965 & 2.900 & 2,19\% & 2.900 & 2,19\% \\ \hline
447.dealII & 37.234 & 29.870 & 19,78\% & 28.779 & 22,71\% \\ \hline
450.soplex & 3.268 & 2.927 & 10,43\% & 2.897 & 11,35\% \\ \hline
464.h264ref & 13.548 & 11.301 & 16,59\% & 11.342 & 16,28\% \\ \hline
473.astar & 903 & 808 & 10,52\% & 806 & 10,74\% \\ \hline
458.sjeng & 2.483 & 2.354 & 5,20\% & 2.190 & 11,80\% \\ \hline
429.mcf & 165 & 164 & 0,61\% & 164 & 0,61\% \\ \hline
471.omnetpp & 1.533 & 1.313 & 14,35\% & 1.313 & 14,35\% \\ \hline
403.gcc & 16.330 & 15.282 & 6,42\% & 15.110 & 7,47\% \\ \hline
445.gobmk & 13.947 & 12.563 & 9,92\% & 12.478 & 10,53\% \\ \hline
462.libquantum & 943 & 820 & 13,04\% & 817 & 13,36\% \\ \hline
401.bzip2 & 2.350 & 1.966 & 16,34\% & 1.966 & 16,34\% \\ \hline
456.hmmer & 3.963 & 3.346 & 15,57\% & 3.304 & 16,63\% \\ \hline
Total (Average) & 6.823 & 5.779 & 18,17\% & 5.676 & 19,09\% \\ \hline
\end{tabular}
\end{small}
\end{center}
\caption{\label{fig:prunningTable}
Prunning analysis.}
\end{figure*}

%Classification analysis
\begin{figure*}[t!]
\begin{center}
\begin{small}
\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
\hline
Name & \multicolumn{1}{l|}{Number of safe instructions} & \multicolumn{1}{l|}{Number of suspicious instructions} & \multicolumn{1}{l|}{Number of uncertain instructions} & \multicolumn{1}{l|}{Number of buggy instructions} & \multicolumn{1}{l|}{Number of suspicious instructions that produced overflows} & \multicolumn{1}{l|}{Percentage of suspicious instructions that produced overflows} & \multicolumn{1}{l|}{Number of Uncertain instructions that produced overflows} & \multicolumn{1}{l|}{Percentage of Uncertain instructions that produced overflows} \\ \hline
470.lbm & 1.138 & 0 & 4 & 0 & 0 & 0,00\% & 0 & 0,00\% \\ \hline
433.milc & 536 & 17 & 1.048 & 0 & 0 & 0,00\% & 11 & 1,05\% \\ \hline
444.namd & 334 & 480 & 2.420 & 0 & 0 & 0,00\% & 12 & 0,50\% \\ \hline
447.dealII & 6.188 & 39 & 28.740 & 0 & 0 & 0,00\% & 50 & 0,17\% \\ \hline
450.soplex & 229 & 16 & 2.881 & 0 & 0 & 0,00\% & 13 & 0,45\% \\ \hline
464.h264ref & 2.539 & 1.195 & 10.147 & 0 & 7 & 0,59\% & 167 & 1,65\% \\ \hline
473.astar & 48 & 11 & 795 & 0 & 0 & 0,00\% & 0 & 0,00\% \\ \hline
458.sjeng & 150 & 213 & 1.977 & 0 & 0 & 0,00\% & 68 & 3,44\% \\ \hline
429.mcf & 1 & 0 & 164 & 0 & 0 & 0,00\% & 8 & 4,88\% \\ \hline
471.omnetpp & 659 & 25 & 1.288 & 0 & 1 & 4,00\% & 2 & 0,16\% \\ \hline
403.gcc & 3.365 & 1.045 & 14.065 & 0 & N/A & N/A & N/A & N/A \\ \hline
445.gobmk & 1.509 & 742 & 11.736 & 0 & 0 & 0,00\% & 4 & 0,03\% \\ \hline
462.libquantum & 104 & 12 & 805 & 0 & 0 & 0,00\% & 7 & 0,87\% \\ \hline
401.bzip2 & 192 & 40 & 1.926 & 0 & N/A & N/A & N/A & N/A \\ \hline
456.hmmer & 663 & 222 & 3.082 & 0 & 0 & 0,00\% & 0 & 0,00\% \\ \hline
\end{tabular}
\end{small}
\end{center}
\caption{\label{fig:classificationTable}
Classification analysis.}
\end{figure*}

\begin{figure}[t!]
\begin{center}
\includegraphics[width=\columnwidth]{images/prunningChart}
\end{center}
\caption{\label{fig:prunningChart}
Chart showing that our analysis was able to avoid inserting 24.93\%
of the instrumentations, in average.}
\end{figure}

%Analysis about the tables

%Analysis about the area chart (Amount of instrumentations pruned)

@@

\begin{figure}[t!]
\begin{center}
\includegraphics[width=\columnwidth]{images/performanceChart}
\end{center}
\caption{\label{fig:performanceChart}
Comparison between the execution times with and without prunning, 
normalized by the original program's execution time.}
\end{figure}

%Performance
Figure~\ref{fig:performanceChart} compares the execution times of the original program (baseline),
the instrumented program without avoiding to insert any instrumentation (black), and 
the instrumented program avoiding to insert the instrumentation whenever possible (gray).
We can see that the maximum overhead we have got was near 10\% in 464.h264ref, a program
that relies heavily on arithmetics instructions. 
As pointed by Dietz {\em et al.}~\cite{Dietz12}, we had some cases where surprisingly we had
a little speedup, too. Nevertheless, the fully instrumented programs had an average slowdown of 3,2\%
and the programs instrumented using the range analysis to do the prunning had an average slowdown
of 1,7\%. That results indicate that even avoiding to insert just 25\% of the overflow checks,
we still can recover almost 50\% of the overhead, because many of the 
analyzed instructions are within loops.
